Hydra Battles in Coq

### 2020-11-20 doc/chapter-powers.tex
redaction chapter-powers

 Variable M : Type.
 Variable mul : M -> M -> M.
 Variable one : M.

 Definition stack := list M.
 Definition config := (M * list M)%type.

 Fixpoint exec (c : code) (x:M) (s: stack) : option config :=
   match c, s with
     nil, _ => Some (x,s)
   | MUL::c, y::s => exec c (mul x y) s
   | SQR::c, s => exec c (mul x x) s
   | PUSH::c, s => exec c x (x::s)
   | SWAP::c, y::z::s => exec c x (z::y::s)
   | _,_ => None
   end.
\end{Coqsrc}

Please define an Euclidean chain generator using this data structure, and prove its correctness (partially solved in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}).
\end{project}

>>>>

 Variable A : Type.
 Variable mul : A -> A -> A.
 Variable one : A.

 Definition stack := list A.
 Definition config := (A * list A)%type.

 Fixpoint exec (c : code) (x:A) (s: stack) : option config :=
   match c, s with
     nil, _ => Some (x,s)
   | MUL::c, y::s => exec c (mul x y) s
   | SQR::c, s => exec c (mul x x) s
   | PUSH::c, s => exec c x (x::s)
   | SWAP::c, y::z::s => exec c x (z::y::s)
   | _,_ => None
   end.

(* ... *)
End Semantics.
\end{Coqsrc}

For instance the chain of Fig.~ \vref{fig:C87} can be represented with the following code:

\begin{Coqsrc}
  PUSH :: PUSH :: SQR  :: MUL :: PUSH :: SWAP :: SQR :: MUL :: PUSH
            :: SWAP :: MUL :: SQR :: SQR :: SQR :: MUL :: nil 
\end{Coqsrc}

Please define an Euclidean chain generator using this data structure, and prove its correctness (partially done  in ~\href{../theories/html/hydras.additions.AM.html}{additions.AM}).
\end{project}
